---
title: "Lab. 05: Harvesting research data"
author: "Sicheng Wang"
date: 2024-02-28
date-modified: today
format:
  html:
    number-sections: true
    toc: true
    toc-depth: 1
bibliography: ../packages.bib
---

<!--

Formatting:

1. You probably don't need to add a header for each of the subsections. It will be a bit easier to read if you just use prose to describe the details under each main header.
2. The main headers should probably be short(er). Including too much information in the header makes it hard to read.

-->

# Data Description

The data to be acquired is the [Switchboard-1 Release 2](https://catalog.ldc.upenn.edu/LDC97S62). The Switchboard corpus contains transcripts of telephone conversations from American English speakers.

The data will be aquired using R. Specifically, the data will be downloaded from the Linguistic Data Consortium (LDC) website using the `download.file()` function and decompressed using the `untar()` function, as the file is in tarball format.

The code will also include functionality to avoid repeated downloads and to document the data acquisition process.

The data license is available at the following link: [LDC User Agreement for Non-Members](https://catalog.ldc.upenn.edu/license/ldc-non-members-agreement.pdf)

# Data Collection Process

## Load packages

<!-- Great job creating .bib entries for these packages! -->

*  Loading `readr`[@readr_p] for writing and reading data.
*  Loading `dplyr`[@dplyr_p] for manipulating data.
*  Loading `fs`[@fs_p] for interacting with file system.

```{r}
#| label: setup-packages
#| message: false

# Load packages
library(readr)
library(dplyr)
library(fs)
```

## Download the data

Download the [SWDA corpus file](https://catalog.ldc.upenn.edu/docs/LDC97S62/swb1_dialogact_annot.tar.gz) and save it in a temporary location. This ensures that when it is unarchived, the compressed file will be automatically removed. To prevent repeated downloads, use an `if` control statement to check if the unarchived file already exists.

```{r}
#| label: download-archive

# URL to SWDA corpus file
file_url <-
  "https://catalog.ldc.upenn.edu/docs/LDC97S62/swb1_dialogact_annot.tar.gz"

# Create a temporary file space for the SWDA corpus file
temp_file <- tempfile()

# The directory of decompressed file
extract_to_dir <- "../data/original/swda/"

# Download SWDA corpus compressed file, if the SWDA corpus has been compressed, no download needed
if (!dir_exists(extract_to_dir)){
  download.file(url = file_url, destfile = temp_file)
  }
```

<!--
It is often easier to read `if` statments if the condition is on a separate line. This is a small thing, but it can make the code easier to read.
-->

## Decompress the data

Unarchive the SWDA corpus file and save it in the directory  `data/original/swda`.

```{r}
#| label: unarchive

# Decompress .zip file and extract to our target directory
if(file_exists(temp_file)) {
  untar(tarfile = temp_file, exdir = extract_to_dir)
  }
```

## Document the data

1. Load `qtalrkit`[@qtalrkit_p] to generate a `data_origin` file for noting the basic information of the data.

```{r}
#| label: creare-data-origin

# Download qtalrkit package
library(qtalrkit)

# Create a data_origin file
if (!file.exists("../data/original/data_origin.csv")) {
  create_data_origin("../data/original/data_origin.csv")
  }
```

<!--
After creating this file template, you will open this file and fill out the relevant information for the SWDA corpus data.

You can edit the CSV file directly in RStudio, or you can navigate to the file on your computer and open it in a text editor or spreadsheet program.
-->

1. Project structure for the SWDA corpus data acquisition

<pre>
project/
├── process/
│   ├── 1_acquire_data.qmd
│   └── ...
├── data/
│   ├── analysis/
│   ├── derived/
│   └── original/
│       ├── data_origin.csv
│       └── swda/
│
├── reports/
├── DESCRIPTION
├── Makefile
└── README
</pre>

<!--
A neat function in the `fs` package is `dir_tree()`. This function can be used to create a tree of the project structure.

```{r}
#| label: dir-tree

# Create a tree of the project structure
dir_tree(path = "../", recurse = 2) # only show the first two levels
```

-->

# Data description

## The resulting data

The extracted data comprises an unarchived folder named `swda/`, which includes one HTML file located in the `doc` folder, along with 14 folders containing `.utt` files.

## Data origin file

```{r}
#| label: read data_origin
#| message: false

#Read data_origin file and assign it to t
data_origin_t <-
  read_csv(file = "../data/original/data_origin.csv")

#Present data_origin
data_origin_t
```
